---
title: "Bayesian linear regression"
author: "Maria Izabel Cavassim Alves"
date: "`r Sys.Date()`"
output:
  md_document:
    variant: markdown_github
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Bayesian Linear Mixed Models
[![Build Status](https://travis-ci.org/MarniTausen/BayzR.svg?branch=master)](https://travis-ci.org/MarniTausen/BayzR)[![Coverage Status](https://coveralls.io/repos/github/MarniTausen/BayzR/badge.svg?branch=master)](https://coveralls.io/github/MarniTausen/BayzR?branch=master)

Here write down the applicability of the software. For more information access the website: <http://www.bayz.biz/>.


# How to install
Bayz can be used in two ways: on a unix/linux/windows prompt, or from
R (available for Mac and Windows). Use from R is limited to some
standard models and is now mostly suited for using smaller data
sets. See the Bayz in R section. Use from a prompt is more versatile
but requires writing a bayz script, examples are in the Bayz2.5
Examples section.


To install this current development version, you first need to install devtools.
```{r, eval=FALSE}
install.packages("devtools")
```

To install the R package on your system you can then use:
```{r, eval=FALSE}
devtools::install_github("MarniTausen/BayzR")
```


# Functions and models associated with BayZ



# Examples

```{r, eval=TRUE}

example_data = data.frame(y = 1:20, x = 20:1)

fit <- bayz(y ~ ranf(x), data=example_data)

summary(fit)

```
